%-------------------------
% Resume in Latex
% Author : Dongyang He
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    %   \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Dongyang He} \\ \vspace{1pt}
    \small dmh5950@psu.edu $|$ \href{https://dongyanghe.netlify.app}{\underline{dongyanghe.netlify.app}} $|$ \href{https://github.com/BlueFireSoul}{\underline{github.com/BlueFireSoul}} 
\end{center}

\section{Profile} % (fold)


\begin{itemize}[leftmargin=0.15in, label={}]
  \item 
  \resumeItemListStart
  \itemsep 0em 
        \resumeItem{Ph.D. Candidate of Economics at Penn State University, adept at applied econometrics and machine learning.}
        \resumeItem{Five-year hands-on experience with demand estimation and causal inference in R, Python, and Stata}
        \resumeItem{Proficient skills in working with large-scale administration data and survey data}
      \resumeItemListEnd
\end{itemize}

% section section_name (end)


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubSubheading
      {\textbf{Pennsylvania State University} $|$ Ph.D. Candidate in Economics (STEM) }{2024 (expected)}
      \resumeItemListStart
        \resumeItem{Fields: Spatial Economics, Applied Econometrics, Applied Microeconomics}
      \resumeItemListEnd
    \resumeSubSubheading
      {\textbf{Pennsylvania State University} $|$ M.A. in Economics, B.S. in Mathematics (Honors)}{2019}
  \resumeSubHeadingListEnd
  

\section{Skills}

    \resumeSubHeadingListStart

    \resumeSubSubheading{\textbf{Economics}}{}
    \resumeItemListStart
      \resumeItem{Structural Estimation: Discrete Choice Model, Dynamic Demand, BLP, Spatial Model}
      \resumeItem{Causal Inference: Diff-in-Diff, Regression Discontinuity, IV }
      \resumeItem{Machine Learning: Regularized Regression, Clustering, Random Forests, Synthetic Control}
      % , Matching, Synthetic Control,A/B Testing
    \resumeItemListEnd

    \resumeSubSubheading{\textbf{Programming} }{}
      \resumeItemListStart
      \resumeItem{Modeling: R, Python, Stata, Matlab, SQL, Shell, ArcGIS, SQL}
    \resumeItemListEnd

    \resumeSubHeadingListEnd

% \vspace{2pt}
\section{Work Experience} % (fold)
\label{sec:working_experience}

\resumeSubHeadingListStart

    % \resumeSubSubheading
    % {\textbf{Instructor} at the Pennsylvania State University}{2023}
    % \resumeItemListStart
    %     \resumeItem{Taught and managed a class of 60 students. }
    % \resumeItemListEnd    
    \resumeSubSubheading
    {\textbf{Research Assistant} for Prof. Michael Gechter}{2022}
    \resumeItemListStart
        \resumeItem{Estimated the effects of cash transfer on school enrollments using a dynamic education demand model.}
        \resumeItem{Utilized high-performance computing infrastructure, ArcGIS, Git, R, and Python. }
    \resumeItemListEnd    
    \resumeSubSubheading
    {\textbf{Short-Term Consultant} at European Bank for Reconstruction and Development}{2019}
    \resumeItemListStart
        \resumeItem{Compiled, cleaned, visualized, and analyzed maps and census data from Mumbai, India.}
        % \resumeItem{Performed and interpreted reduced-form analysis with Stata. }
        \resumeItem{Coordinated regularly with three other researchers to deliver timely results.}
    \resumeItemListEnd
    
\resumeSubHeadingListEnd
% section working_experience (end)


\section{Research Experience}
    \resumeSubHeadingListStart

    \resumeSubSubheading
    {\textbf{Distributional Impacts of Exclusionary Zoning Policies}}{2023}
    \resumeItemListStart
        \resumeItem{Investigated the differential impacts of density and height regulations across income groups in the greater Boston area, using large-scale parcel-level housing data covering 1 million residential properties.}
        \resumeItem{Conducted spatial discontinuity design to examine the impact of zoning restrictions on housing supply and demographic composition. }
        \resumeItem{Developed a theoretical housing production model to rationalize the impacts and interactions of density and height regulations on housing supply. }
        \resumeItem{Developed a discrete choice model to estimate preferences of heterogenous households over locations and housing.}
    \resumeItemListEnd

    \resumeSubSubheading
    {\textbf{Migration and Proximity Preference in Fertility Decision}}{2022}
    \resumeItemListStart
        \resumeItem{Examined how distance from hometown might impact people's fertility decision, using large-scale survey data covering 5 million households in the U.S. from 2000 to 2019.}
        \resumeItem{Developed a discrete choice model to estimate households' preferences over locations, fertility choices, and consumption. }
        \resumeItem{Found that changes in migration pattern can account for 5\% of the changes in fertility rate since 2000.  }
    \resumeItemListEnd
    
    \resumeSubSubheading
    {\textbf{Industrial Payments and Physicians’ Prescriptions}}{2020}
    \resumeItemListStart
        \resumeItem{Investigate the impact of industrial payments on physicians' prescription choices in the Statin market, using over 10 million prescription records from 16,000 physicians during 2016 and 2017. }
        \resumeItem{Implement a split-sample Lasso approach to systematically select controls and instruments from a large potential set for demand estimation. }
    \resumeItemListEnd
    
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------

\section{Leadership and Honors}
  \resumeSubHeadingListStart
  
  \resumeSubSubheading
      {Founder and Organizer of International Trade Reading Group, Penn State}{2020 -- Present}

  \resumeSubSubheading{Schreyer Scholar, Penn State}{2019}
    \resumeSubSubheading{Bates \& White Research Funding}{2018}
    \resumeSubSubheading{Mathematics Advanced Study Semesters Fellowship}{2017}


  \resumeSubHeadingListEnd

%-----------PROJECTS-----------



%
%-----------PROGRAMMING SKILLS-----------




% \section{Technical Skills}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%     \textbf{Economics}{: Demand Estimation, Discrete Choice Model, Dynamic Model, Causal Inference} \\
%      \textbf{Languages}{: R (Shiny), Julia, Python, Stata, Matlab} \\
%      \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
%      \textbf{Developer Tools}{: Git, Docker, TravisCI, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
%      \textbf{Libraries}{: pandas, NumPy, Matplotlib}
%     }}
%  \end{itemize}


%-------------------------------------------
\end{document}
