\section{Research Experience}
    \resumeSubHeadingListStart

    \resumeSubSubheading
    {\textbf{Distributional Impacts of Exclusionary Zoning Policies}}{2023}
    \resumeItemListStart
        \resumeItem{Investigated the differential impacts of density and height regulations across income groups in the greater Boston area, using large-scale parcel-level housing data covering 1 million residential properties.}
        \resumeItem{Employed spatial discontinuity design to examine the impact of zoning restrictions on housing supply and demographic composition. }
        \resumeItem{Formulated a theoretical housing production model to rationalize the impacts and interactions of density and height regulations on housing supply. }
        \resumeItem{Developed a discrete choice model to estimate preferences of heterogenous households over locations and housing.}
    \resumeItemListEnd

    \resumeSubSubheading
    {\textbf{Migration and Proximity Preference in Fertility Decision}}{2022}
    \resumeItemListStart
        \resumeItem{Examined how distance from hometown might impact people's fertility decision, using large-scale survey data covering 5 million households in the U.S. from 2000 to 2019.}
        \resumeItem{Constructed a discrete choice model to estimate households' preferences over locations, fertility choices, and consumption. }
        \resumeItem{Discovered that changes in migration pattern can account for 5\% of the changes in fertility rate since 2000.  }
    \resumeItemListEnd
    
    \resumeSubSubheading
    {\textbf{Industrial Payments and Physicians’ Prescriptions}}{2020}
    \resumeItemListStart
        \resumeItem{Explored the impact of industrial payments on physicians' prescription choices in the Statin market, using over 10 million prescription records from 16,000 physicians during 2016 and 2017. }
        \resumeItem{Applied a split-sample Lasso approach to systematically select controls and instruments from around 500 potential variables for demand estimation. }
    \resumeItemListEnd
    
    \resumeSubHeadingListEnd